### 2018-03-14 paper/sexSelectionSpacing-ver1.tex
Add high education conditional survival curve results

What is most remarkable about the second spell conditional survival curve for 
urban women with eight or more years of education, shown in Figure \ref{fig:pps_high}, 
is that the distribution of spacing is almost indistinguishable from that of rural 
women with no education for the 1972--1984 period.
This points to these two very different groups of women behaving in a similar fashion
in response to son preference in a situation where there was little access to
prenatal sex determination or little incentive to use it early even for those 
who might have had access.
Whereas the no education group show almost no change across the four decades,
the high education women show a rightward shift if the spacing pattern when
the first child is a girl.
The result is that the spacing patterns are close to identical for the first-born 
a girl and the first-born a boy.

@@

>>>>

The distribution of spacing, shown in Figure \ref{fig:pps_high}, for the second spell 
conditional survival curve for urban women with eight or more years of education 
is almost indistinguishable from that of rural women with no education 
for the 1972--1984 period.
This points to these two very different groups of women behaving in a similar fashion
in response to son preference in a situation where there was little access to
prenatal sex determination or little incentive to use it early even for those 
who might have had access.

Whereas the no education group show almost no change across the four decades,
the high education women show a rightward shift if the spacing pattern when
the first child is a girl.
The result is that the spacing patterns are close to identical after first-born 
girls and after first-born boys.
Given the elevated predicted percentage boys show in Table 
\ref{tab:median_sex_ratio_high} this change is consistent with use of 
sex selection for women with a girl as their first child.

The hypothesized correlation between use of sex selection and reversal of 
the standard spacing pattern show up clearly in the 2005--2016 period for the 
third spell with spacing to the third child consistently longer with two girls 
than with either two girls or one boy and one girl.
The rightward movement for only girls from the, mostly, standard pattern in 
the 1972--1984 period to the new pattern in the 2005--2016 period is substantial.
There is also indications that the spacing distribution has moved rightward
for women with one boy and one girl relatively to women with two boys, which
provides some evidence for use of sex selection for this group.
The caveat is that the 1972--1985 period also had an biased sex ratio, which
points to uncorrected recall error for this group.

There is a even more pronounced rightward shift for spacing after only girls
in the fourth spell, although these results are based on fewer births, especially
for women with two or more sons.%
\footnote{
As mentioned, it is possible that some women had access to sex selection even
in the first period.
I would expect well educated urban women with more children to be the
most likely to know about and use this early access to prenatal sex determination.
}
Furthermore, the differences are large across most of the distribution.
Twelve months after the beginning of the spell there is an approximately ten 
percentage points difference in the conditional survival curves for only girls
and only boys.
That is, of the women who are predicted to have a fourth child just over 30\%
of women with three boys have had their fourth child, while less than 20\% of
those with three girls have had theirs.
Even at three years after the spell there is a more than five percentage
points difference.

As discussed above there is some evidence of a two-son preference with
the spacing pattern almost the same for women with three boys and with
two boys and one girl.
The conditional survival curve for women with one boy and two girls is
consistently above those with two or more son, but below those with
three girls.
This fit the predicted sex ratios shown above where the highest
predicted sex ratio is for women with only girls, followed by those
with one son and two girls, and those with two or more boys having
almost the same sex ratio.

@@

[

using conditional survival curves forces everybody to finish at the 
same month.
How many births are there?
We can show that using standard survival curves.
The flatter the curve the fewer births.

72 months = 6 years, plus the 9 months from the previous birth.
]
